Trends in Preventive Care Practices among US Adults with Diabetes, 2008-2020 

### 2022-12-29 scripts/manuscript/manuscript_draft.qmd
For remote syncing

cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata')) %>% 
  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
                          TRUE ~ AAPC),
         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
                                    TRUE ~ `APC Period 1`)) %>%
  # Rename poverty levels
  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ 'Income < 100% of the poverty line',
                            as.character(strata) == 'Low income' ~ 'Income 100% - 199% of the poverty line',
                            as.character(strata) == 'Middle income' ~ 'Income 200% - 399% of the poverty line',
                            as.character(strata) == 'High income' ~ 'Income > 400% of the poverty line',
                            TRUE ~ as.character(strata)))

preventive_practice_table <- cleaned_preventive_df %>% 
  group_by(stratifier) %>%
  select(stratifier, strata, `2008`:`2020`, `Percent Change`, `Joinpoint Year` = segment,
         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
  gt() %>% 
  sub_missing(missing_text = ' ')
preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
preventive_practice_table %>% 
  gtsave('preventive_practices.docx')
```

@@

```{r}
tar_load(age_adjusted_stats)

stats_table_plot_dat <- age_adjusted_stats %>% 
  filter(strata != 'Total') %>%
  filter(strata != 'Not available') %>% 
  filter(strata != 'Other Race/Not Hispanic') %>% 
  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
                                   variable == 'DENT_all' ~ '1 or more dentist visits',
                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
                                   variable == 'flu' ~ 'Received flu vaccine',
                                   variable == 'foot' ~ 'Foot examination'),
         strata = case_when(strata == 'stat_0' ~ 'Overall',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  split(., f = .$stratifier)

@@

overall_data <- stats_table_plot_dat$overall
# Remove the overall data from the list
stats_table_plot_dat <- stats_table_plot_dat[-4]
# Relevel the poverty factors
stats_table_plot_dat$poverty$strata <- factor(stats_table_plot_dat$poverty$strata, levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'))
test_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_smooth( se = FALSE) +
      geom_smooth(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = age_adjusted_prop * 100),
                  color = 'black',
                  se = FALSE,
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(00, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
      labs(x = 'Year', y = 'Percentage')
  )

test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') 
test_plots[[2]] <- test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
test_plots[[3]] <- test_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
test_plots[[4]] <- test_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
test_plots[[5]] <- test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
                                                                             strip.text = element_blank())
test_plots[[6]] <- test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
test_plots <- list(
  test_plots[[1]],
  test_plots[[6]],
  test_plots[[5]],
  test_plots[[2]],
  test_plots[[3]],
  test_plots[[4]]
)

exam_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_smooth(se = FALSE) +
      geom_smooth(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = age_adjusted_prop * 100),
                  color = 'black',
                  se = FALSE,
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(  0, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95)) +
      labs(x = 'Year', y = 'Percentage')
  )

exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)')
exam_plots[[2]] <- exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
exam_plots[[3]] <- exam_plots[[3]] + labs(color = "Insurance") + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
exam_plots[[4]] <- exam_plots[[4]] + labs(color = 'Poverty') + theme(strip.background =  element_blank(),
                                                                            strip.text = element_blank())
exam_plots[[5]] <- exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(strip.background =  element_blank(),
                                                                             strip.text = element_blank())
exam_plots[[6]] <- exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                                          strip.text = element_blank())
exam_plots <- list(
  exam_plots[[1]],
  exam_plots[[6]],
  exam_plots[[5]],
  exam_plots[[2]],
  exam_plots[[3]],
  exam_plots[[4]]
)
(all_exam_plots <- exam_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
(all_test_plots <- test_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
ggsave(plot = all_exam_plots,
       filename = 'figures/all_exam_plots.tiff',
       dpi = 200)
ggsave(plot = all_test_plots,
       filename = 'figures/all_test_plots.tiff',
       dpi = 200)
```

>>>>

cleaned_preventive_df <- left_join(clean_age_adjusted, cleaned_jp_apc, by = c('stratifier', 'strata')) %>% 
  mutate(AAPC = case_when(is.na(AAPC) & is.na(`APC Period 2`) ~ `APC Period 1`,
                          TRUE ~ AAPC),
         `APC Period 1` = case_when(is.na(`APC Period 1`) & is.na(`APC Period 2`) ~ AAPC,
                                    TRUE ~ `APC Period 1`)) %>%
  # Rename poverty levels
  mutate(strata = case_when(as.character(strata) == 'Poor/Negative' ~ '< 100%',
                            as.character(strata) == 'Low income' ~ '100% - 199%',
                            as.character(strata) == 'Middle income' ~ '200% - 399%',
                            as.character(strata) == 'High income' ~ '> 400%',
                            TRUE ~ as.character(strata)))

preventive_practice_table <- cleaned_preventive_df %>% 
  group_by(stratifier) %>%
  select(stratifier, strata, `2008`:`2020`, `Percent Change`, `Joinpoint Year` = segment,
         `APC Period 1`, `APC Period 2`, `AAPC`) %>%
  mutate(stratifier = case_when(as.character(stratifier) == 'Poverty level' ~ 'Income as % of poverty line',
                                TRUE ~ as.character(stratifier))) %>% 
  gt() %>% 
  sub_missing(missing_text = ' ')
preventive_practice_table$`_data` <- preventive_practice_table$`_data`[c(1:18, 20, 19, 21), ]
preventive_practice_table %>% 
  gtsave('preventive_practices.docx')
```

@@

```{r}
tar_load(age_adjusted_stats)
tar_load(jp_proportion_plot_data)

stats_table_plot_dat <- jp_proportion_plot_data %>% 
  filter(strata != 'Total') %>%
  filter(strata != 'Not available') %>% 
  filter(strata != 'Other Race/Not Hispanic') %>% 
  mutate(variable_text = case_when(variable == 'a1c' ~ '2 or more A1C tests',
                                   variable == 'CHOL_all' ~ 'Cholesterol tested',
                                   variable == 'DENT_all' ~ '1 or more dentist visits',
                                   variable == 'eye-exam' ~ 'Eye exam with dilation',
                                   variable == 'flu' ~ 'Received flu vaccine',
                                   variable == 'foot' ~ 'Foot examination'),
         strata = case_when(strata == 'stat_0' ~ 'Overall',
                            TRUE ~ strata)) %>% 
  mutate(strata = as.factor(strata)) %>% 
  split(., f = .$stratifier)

@@

overall_data <- stats_table_plot_dat$overall
# Remove the overall data from the list
stats_table_plot_dat <- stats_table_plot_dat[-4]
# Relevel the poverty factors
stats_table_plot_dat$poverty$strata <-
  factor(
    stats_table_plot_dat$poverty$strata,
    levels = c('High income', 'Middle income', 'Low income', 'Poor/Negative'),
    labels = c(
      '> 400% ',
      '200% - 399%',
      '100% - 199%',
      '< 100%'

    )
  )
test_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
      geom_line(data = filter(overall_data, variable %in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = model * 100),
                  color = 'black',
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(00, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
            legend.title = element_text(size = 8),
            legend.text = element_text(size = 6)) +
      labs(x = 'Year', y = 'Percentage')
  )

test_plots[[1]] <- test_plots[[1]] + labs(color = 'Age (grouped)') +
  theme(axis.title.x = element_blank())
test_plots[[2]] <-
  test_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[3]] <-
  test_plots[[3]] + labs(color = "Insurance") + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[4]] <-
  test_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank()
  )
test_plots[[5]] <-
  test_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
test_plots[[6]] <-
  test_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                strip.text = element_blank(),
    axis.title.x = element_blank())
test_plots <- list(
  test_plots[[1]],
  test_plots[[6]],
  test_plots[[5]],
  test_plots[[2]],
  test_plots[[3]],
  test_plots[[4]]
)

exam_plots <- stats_table_plot_dat %>% 
   map(
    ~ ggplot(filter(.x, variable %!in% c('a1c', 'CHOL_all', 'flu')),
             aes(
      x = year,
      y = age_adjusted_prop * 100,
      group = strata,
      color = strata
    )) +
      #geom_point() +
      geom_line(aes(x = year, y = model * 100, group = strata, color = strata)) +
      geom_line(data = filter(overall_data, variable %!in% c('a1c', 'CHOL_all', 'flu')),
                  aes(x = year, y = model * 100),
                  color = 'black',
                  linetype = 'dashed') +
      facet_wrap( ~ variable_text, ncol = 3) +
      theme_classic() +
      scale_y_continuous(
        limits = c(  0, 100),
        breaks = seq(0, 100, 25),
        labels = seq(0, 100, 25)
      ) +
      scale_x_continuous(
        limits = c(2008, 2020),
        breaks = seq(2008, 2020, 2),
        labels = seq(2008, 2020, 2)
      ) +
      scale_color_brewer(type = 'qual', palette = 'Set2') +
      theme(axis.text = element_text(color = 'black'),
            axis.text.x = element_text(angle = 45, hjust = 0.9, vjust = 0.95),
            legend.title = element_text(size = 8),
            legend.text = element_text(size = 6)) +
      labs(x = 'Year', y = 'Percentage')
  )

exam_plots[[1]] <- exam_plots[[1]] + labs(color = 'Age (grouped)') +
  theme(axis.title.x = element_blank())
exam_plots[[2]] <-
  exam_plots[[2]] + labs(color = 'Highest degree \nobtained') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
exam_plots[[3]] <-
  exam_plots[[3]] + labs(color = "Insurance") + theme(
    strip.background =  element_blank(),
    strip.text = element_blank(),
    axis.title.x = element_blank()
  )
exam_plots[[4]] <-
  exam_plots[[4]] + labs(color = 'Income as % of \npoverty line') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank()
  )
exam_plots[[5]] <-
  exam_plots[[5]] + labs(color = 'Race/Ethnicity') + theme(
    strip.background =  element_blank(),
    strip.text = element_blank()
  )
exam_plots[[6]] <-
  exam_plots[[6]] + labs(color = 'Sex') + theme(strip.background =  element_blank(),
                                                strip.text = element_blank(),
    axis.title.x = element_blank())
exam_plots <- list(
  exam_plots[[1]],
  exam_plots[[6]],
  exam_plots[[5]],
  exam_plots[[2]],
  exam_plots[[3]],
  exam_plots[[4]]
)
(all_exam_plots <- exam_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
(all_test_plots <- test_plots %>% 
  wrap_plots(nrow = 6) &
  theme(plot.margin = margin(0.5, 0.5, 0.5, 0.5, 'pt')))
ggsave(plot = all_exam_plots,
       filename = 'figures/all_exam_plots.tiff',
       dpi = 200,
       width = 10,
       height = 7)
ggsave(plot = all_test_plots,
       filename = 'figures/all_test_plots.tiff',
       dpi = 200,
       width = 10,
       height = 7)
ggsave(plot = all_exam_plots,
       filename = 'figures/all_exam_plots.svg',
       dpi = 200,
       width = 10,
       height = 7)
ggsave(plot = all_test_plots,
       filename = 'figures/all_test_plots.svg',
       dpi = 200,
       width = 10,
       height = 7)
```
